### 2021-09-24 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_betadiversity_response@9eca1242e2389cdc5ed5ec693adae6b6a0d1ce29 🚀

Despite having established its usefulness in the last ten years, the
decomposition of ecological networks in components allowing to measure
their \(eta\)-diversity retains some methodological ambiguities.
Notably, how to quantify the relative effect of mechanisms tied to
interaction rewiring \emph{vs.} species turnover has been interpreted
differently by different authors. In this contribution, I present
mathematical arguments and numerical experiments that should (i)
establish that the decomposition of networks as it is currently done is
indeed fit for purpose, and (ii) provide guidelines to interpret the
values of the components tied to turnover and rewiring.

@@

In conclusion, this numerical experiment shows that the decomposition as
initially presented by Poisot \emph{et al.} (2012), \emph{i.e.} using
denominators that make sense from a network composition point of view,
succeeds at capturing the relative effect of turnover and rewiring.
\#\#\# Numerical experiment: the decomposition captures the roles of
species turnover and connectance accurately

@@

\newpage

\hypertarget{references}{%
\subsection{References}\label{references}}

\singlespacing

>>>>

Despite having established its usefulness in the last ten years, the
decomposition of ecological networks in components allowing to measure
their \(\beta\)-diversity retains some methodological ambiguities.
Notably, how to quantify the relative effect of mechanisms tied to
interaction rewiring \emph{vs.} species turnover has been interpreted
differently by different authors. In this contribution, I present
mathematical arguments and numerical experiments that should (i)
establish that the decomposition of networks as it is currently done is
indeed fit for purpose, and (ii) provide guidelines to interpret the
values of the components tied to turnover and rewiring.

@@

In conclusion, this numerical experiment shows that the decomposition as
initially presented by Poisot \emph{et al.} (2012), \emph{i.e.} using
denominators that make sense from a network composition point of view,
succeeds at capturing the relative effect of turnover and rewiring.

\hypertarget{numerical-experiment-the-decomposition-captures-the-roles-of-species-turnover-and-connectance-accurately}{%
\subsubsection{Numerical experiment: the decomposition captures the
roles of species turnover and connectance
accurately}\label{numerical-experiment-the-decomposition-captures-the-roles-of-species-turnover-and-connectance-accurately}}

@@

\hypertarget{references}{%
\subsection*{References}\label{references}}
\addcontentsline{toc}{subsection}{References}
